%-------------------------
% Resume in Latex
% Author : Mitul Savani
% Website: https://mitulsavani.com/
% License : MIT
%------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \vspace{-1pt}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://mitulsavani.com/}{\LARGE Mitul Savani}} & \href{https://mitulsavani.github.io/}{Portfolio: \textbf{mitulsavani.com}}\\ 
  \href{mailto:mitul.savani1@gmail.com}{mitul.savani1@gmail.com} & {\href{https://github.com/mitulsavani}{github.com/\textbf{mitulsavani}}} \\
  {415-734-1688} & {San Francisco, CA}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Francisco State University}{\textit{Jan 2016 - May 2020}}
      {Bachelor's of Science in Computer Science}{GPA 3.82}
      \resumeItemListStart
        \resumeItem{Coursework: }
          {Data Structures \& Analysis of Algorithms | Database System Design | Internet Application Design \& Development | Mobile Application Development | Human-Computer Interaction | Programming Methodology}
      \resumeItem{Dean's Scholar List: }
          {Year 2016, Year 2017, Spring 2018}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Software Engineer}{San Francisco, CA}
      {Kandou}{Nov. 2019 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Expertise in UI/Front-End Development, developing features, and designing user interaction screens.}
        \resumeItem{}
          {Responsible for beta testing and releasing iOS and Android applications to 500+ active users on app stores.}
        \resumeItem{}
          {Working in an agile environment consisting of analyzing users and peer feedback on the submitted work.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Development Intern \& Undergraduate Researcher}{San Francisco, CA}
      {Claryty | Bioinformatics Research Project by Stanford University}{Nov. 2018 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Developed a new mobile application for consumers with React Native/Redux that presents adverse effect reports for prescription drugs.}
        \resumeItem{}
          {Designed the full architecture of software stack in order to scale future Food and Drug Administration(FDA) data sets and user input.}
        \resumeItem{}
          {Involved in weekly SCRUM meetings to keep track of the ongoing project status and issues.}
        \resumeItem{}
          {Won 3rd prize out of 240 projects at the College of Science and Engineering annual showcase in 2019 at SF State.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Open Source Contributor}{}
      {Facebook | React Native Core, React Native Website}{}
      \resumeItemListStart
        \resumeItem{}
          {Updated API and Component docs to reflect the props and methods reflected in core repository(v62).}
        \resumeItem{}
          {Contributed in migrating ImageStore native module into the new TurboModule System architecture of the repository(v59).}
        \resumeItem{}
          {Added 50+ libraries associated with Analytics, Geolocation, Deep Link, Other Platforms, and UI to the RN directory.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
  
%-----------LEADERSHIP ACTIVITIES-----------------
\section{Leadership Activities}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Founder  - Tutoring Services}{San Francisco, CA}
      {Association of Computing Machinery at SF State}{Aug. 2017 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Consulted with students in their side projects and assignments by showing them the effective use of standard data structures and algorithms; TA for 140 hours a semester.}
        \resumeItem{}
          {Improved overall academic performance of incoming freshmen and sophomores by 30\% in core courses such as Programming Methodology and Software Development.}
        \resumeItem{}
          {Recruited, organized, and trained tutors for the Computer Science Department.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Hackathon Organizer}{San Francisco, CA}
      {SF Hacks}{Nov. 2017 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Arranged first collegiate Hackathon in San Francisco with over 350 attendees.}
        \resumeItem{}
          {Spearhead an outreach team to reach out to 30+ companies for partnership and raised \$18,000 in sponsorship.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Teaching Assistant}{San Francisco, CA}
      {MobileSpace | React Native Bootcamp}{Feb. 2018 - Apr. 2018}
      \resumeItemListStart
        \resumeItem{}
          {Took initiative in learning React Native and went on to successfully develop 2 functional apps under minimal supervision.}
        \resumeItem{}
          {Facilitated a dynamic and collaborative classroom of 15 students and conducted weekly office hours for further assistance.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd
   
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {Spiral}{}
      {Point of Sale(POS) application system with cryptocurrency wallet for local businesses}{}
      \resumeItemListStart
        \resumeItem{}
          {Precise transaction was acquired using CryptoCompare API to fetch the latest cryptocurrency price.}
        \resumeItem{}
          {Managed stand up meetings and assigned sprints to increase work flow throughout the team of 3 engineers.}
        \resumeItem{}
          {Designed 10+ screens to build core features of the product and shipped it within 4 weeks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Programming Languages:}{ JavaScript, Java, Python, Ruby, C++, C, HTML/CSS}
    }
    \item{
     \textbf{Frameworks:}{ React, React Native, Redux, MobX, Vue, Node.js, Express.js, Java Swing}
    }
    \item{
     \textbf{Databases and Infrastructure:}{ MySQL, PostgreSQL, AWS, Google Cloud Platform(GCP)}
    }
     \item{
     \textbf{Tools \& Miscellaneous:}{ Git, bash, NPM, Yarn, REST API, Docker, Postman, Lottie, Jira, Trello, Classical Algorithms \& Data Structures, AirBnB code standards}
    }
 \resumeSubHeadingListEnd
 

\end{document}